### 2019-03-16 papers/journal/intro.tex
added missing file

Previous analyses of vesicle traffic networks dealt with this combinatorial
explosion by using a sampling approach~\cite{mani2016stacking}. 
%
In these analyses, vesicle traffic is modelled as an update system. 
%
%The traffic rule specifies how the system transitions from one
%time point to the next. 
%
Given a traffic rule and an initial condition, the system is updates one step a time, updating molecular flux of the compartments, until a steady state is reached. 
%
The update rule defines the flux transition for the next step. 
%
By studying a large sample of randomly generated update rules, such analyses can make statistical claims about vesicle traffic. 
%

>>>>

Previous analyses of vesicle traffic networks dealt with this combinatorial
explosion by using a sampling approach~\cite{mani2016stacking}. 
%
In these analyses, vesicle traffic is modelled as an update system. 
%
%The traffic rule specifies how the system transitions from one
%time point to the next. 
%
Given a traffic rule and an initial condition, the system updates molecular flux of the compartments one step a time choosing one among the possibly exponential choices of the rule.
%
The update rule defines the flux transition for the next step. 
%
This process is performed until a steady state is reached. 
%
%
By studying a large sample of randomly generated update rules, such analyses can make statistical claims about vesicle traffic. 
%
